---
title: "A Report on Lake Ontario's Microbes"
author: "Dilmini Alahakoon"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

In this report, we analyze how different water quality parameters affect the abundance of the bacteria phyla.

# Set-up

#### Loading packages

First, we'll load necessary packages.

```{r packages, message=FALSE, warning=FALSE}

library(tidyverse)

```

# Data

Then, we'll read in our data and produce data frame.

```{r data, message = FALSE, warning = FALSE}
sample_and_taxon <- read_csv("data/sample_and_taxon.csv")
```

# Analyzing the data

Then, we plot the relationship between temperature and microbial cell abundance.

```{r cells_va_temp}

sample_and_taxon %>% 
  ggplot() +
  aes(x = temperature,
      y = cells_per_ml/1e6,
      colour = env_group) +
  geom_point() +
  labs(x = "Temperature (C)",
       y = "Cells (million/ml)",
       title = "Are temperature and cell abundance linked?")

```

It apprears that there is a positive relationship.

```{r data_summary, include=FALSE}

nSamples <- nrow(sample_and_taxon)

minTemp <- sample_and_taxon %>%
  pull(temperature) %>%
  min() %>%
  round()

maxTemp <- sample_and_taxon %>%
  pull(temperature) %>%
  max() %>%
  round()

```

The above plot shows `r nSamples` samples. For these samples the minimum temperature was `r minTemp` C and maximum temperature `r maxTemp` C.

```{r kable}
library(knitr)

sample_and_taxon %>%
  filter(env_group == "Deep") %>%
  select(cells_per_ml,temperature,Chloroflexi) %>%
  kable()
```

#### Comments:

-   *Comment 1*:
-   **Comment 2**:
-   ***Comment 3***:

1.  Comments:
2.  Comments:

### Adding hyperlink

Please read this [Markdown](https://rmarkdown.rstudio.com/authoring_basics.html)


 
 
 | Statistic           | Value       |
 |---------------------|-------------|
 | Number of samples   | `r nSamples` |
 | Minimum temperature | `r minTemp` |
 | Maximum temperature | `r maxTemp` |




